Age-related changes in plant growth and traits

### 2016-09-19 scripts/Accessory_figs_20160905.Rmd
work on accessory costs ms

plot(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(.1,5000),ylim=c(0.001,50))
mod <- sma(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",slope=1,method="OLS")
summary(mod)
line_function_log_xy(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$scaled_bud_count,mod,1)

plot(scaled_bud_count ~ seedset, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))

@@

#proportion energy invested in accessory tissues unrelated to seedsize
mod <- sma(seed_size ~ prop_accessory_ee, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="y",slope.test=1)
summary(mod)
plot(seed_size ~ prop_accessory_ee, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))

@@

@@

plot(scaled_seed_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species))
points(scaled_bud_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("count, scaled to plant size",2,line=2.3)
mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="OLS")
mod2 <- sma(scaled_bud_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_bud_count!=0),log="xy",slope=3.23,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

@@

plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("count, scaled to plant size",2,line=2.3)
mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

>>>>

pdf("figs2/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
plot

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
options(scipen = 5)

mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]],species!="PEPU"),method="OLS", log="xy",slope.test=-1)
mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0)

#mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
summary(mod1)
plot(success_inv ~ prepollen_success_inv, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(10,100000),ylim=c(10,100000))
mod <- sma(success_inv ~ prepollen_success_inv, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
line_function_log_xy(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)

SummaryInd$ovule_ratio <- SummaryInd$prepollen_costs/SummaryInd$embryo_endo_size

SummarySpp[["mean"]]$pre_pollen_all_inv_scaled <- SummarySpp[["mean"]]$prepollen_all_inv /SummarySpp[["mean"]]$leaf_area

plot(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
mod <- sma(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",slope=1, method="OLS")
summary(mod)

plot(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
mod <- sma(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",slope=1, method="OLS")

dev.off()

@@

#RE per seed unrelated to seedsize
mod <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
summary(mod)
plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

#energy invested in accessory tissues unrelated to seedsize
mod <- sma(accessory_per_seed_using_ee ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
summary(mod)
plot(accessory_per_seed_using_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

#total seed costs unrelated to seedsize
mod <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
summary(mod)
plot(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

#failure per seed unrelated to seedsize
mod <- sma(failure_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
summary(mod)
plot(failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

mod <- sma(prop_prepollen_costs ~ seedset, data=subset(SummarySpp[["mean"]]),method="OLS", log="x",slope.test=1)
summary(mod)
plot(prop_prepollen_costs ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))

mod <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
summary(mod)
plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
summary(mod)
plot(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

mod <- sma(scaled_seed_count ~ provisioning_costs, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
summary(mod)
plot(scaled_seed_count ~ provisioning_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

mod <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
summary(mod)
plot(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

mod <- sma(prepollen_all_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
summary(mod)
plot(prepollen_failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
points(prepollen_costs~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))

@@

#scaled ovule production vs prop pollen attraction  - all species
mod <- sma(prop_prepollen_costs~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
summary(mod)
plot(prop_prepollen_costs ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

@@

plot(scaled_seed_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species))
points(scaled_ovule_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("count, scaled to plant size",2,line=2.3)
mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="OLS")
mod2 <- sma(scaled_ovule_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_ovule_count!=0),log="xy",slope=3.23,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

@@

plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
points(scaled_ovule_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("count, scaled to plant size",2,line=2.3)
mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
mod2 <- sma(scaled_ovule_count~embryo_endo_size,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",slope=-1,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
